---
title: "Homework 6"
author: "Yue Liu"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data 

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1
    )
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL")%>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

start with one city

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

# generalized regression model
glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>%  # need to specify distribution
  broom::tidy() %>% # estimate is reported as log odds ratio; race shows in 5 subgroups
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 2

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(babysex = as.factor(case_when(babysex == 1 ~ "male", 
                                       babysex == 2 ~ "female")),
         frace = as.factor(case_when(frace == 1 ~ "White",
                                     frace == 2 ~ "Black",
                                     frace == 3 ~ "Asian",
                                     frace == 4 ~ "Puero Rican",
                                     frace == 8 ~ "Other",
                                     frace == 9 ~ "Unknown")),
         malform = as.factor(case_when(malform == 0 ~ "absent",
                                       malform == 1 ~ "present")),
         mrace = as.factor(case_when(mrace == 1 ~ "White",
                                     mrace == 2 ~ "Black",
                                     mrace == 3 ~ "Asian",
                                     mrace == 4 ~ "Puero Rican",
                                     mrace == 8 ~ "Other",
                                     mrace == 9 ~ "Unknown"))
         )
```

Import dataset and convert `babysex`, `frace`(father's race), `mrace`(mother's race), and `malform`(presence of malformations) to factor. 

Since there is no further information on which predictors might be more significant, I used backward stepwise regression to select variables.

```{r}
my_model = lm(bwt ~ ., data = birthweight_df) %>% 
  step(direction = 'backward', trace = 0)

summary(my_model)

# glm(bwt ~ ., data = birthweight_df) %>% 
#   step(direction = 'both',
#        scope = list(lower = . ~ 1,
#                     uppwer = .~.^2),
#        trace = 0)
# 
# terms(my_model) %>% 
#   attr("term.labels") %>% 
#   str_c(., collapse =  "+") %>% 
#   str_c("bwt ~ ",.) %>% 
#   as.formula()
```

According to the results, my model will contain predictors `babysex`, `bhead`(baby's head circumference), `blength` (baby's length at birth), `delwt`(mother's weight), `fincome`(family monthly income), `gaweeks`(gestational age in weeks), `mheight`(mother's height), `mrace`(mother's race), `parity`(number of live births prior to this pregnancy), `ppwt` (mother's pre-preg weight), and `smoken` (average numbers of cigarettes smoked during pregnancy)

Plot of model residuals against fitted values.

```{r}
ggplot() +
  geom_point( 
    data = birthweight_df %>% 
      add_residuals(my_model) %>% 
      add_predictions(my_model),
    alpha = 0.5) +
  aes(x = pred, y = resid) +
  labs(title = "Residual Plot",  
       x = "Predicted/Fitted value", 
       y = "Residual") 
```

cross validation using `modelr`

```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))

cv_df = 
  cv_df %>% 
  mutate(
    my_mod = map(.x = train, ~ lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt +smoken, data = .x)),
    mod_1 = map(.x = train, ~ lm(bwt ~ blength + gaweeks, data = .x)),
    mod_2 = map(.x = train, ~ lm(bwt ~ blength * bhead * babysex, data = .x))
    ) %>%
  mutate(
    rmse_my = map2_dbl(.x = my_mod, .y = test, ~rmse(model = .x, data = .y)),
    rmse_1 = map2_dbl(.x = mod_1, .y = test, ~rmse(model = .x, data = .y)),
    rmse_2 = map2_dbl(.x = mod_2, .y = test, ~rmse(model = .x, data = .y))
)
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) +
  geom_violin()
```

```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  group_by(model) %>% 
  summarize(avg_rmse = mean(rmse))
```

## Problem 3

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

```{r}
boot_results = 
  weather_df %>% 
  bootstrap(100, id = "strap_number") %>% 
  mutate(
    models = map(.x = strap, ~ lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  unnest(results) %>% 
  mutate(r_square = map(models, broom::glance)) %>% 
  select(strap_number, term, estimate, r_square) %>% 
  unnest(r_square) %>% 
  select(strap_number, term, estimate, r.squared)
```

```{r}
boot_results = 
  boot_results %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  janitor::clean_names() %>% 
  mutate(log = log(tmin*intercept))
```

Distribution plot of $$\hat r^2$$

```{r}
boot_results %>% 
  ggplot(aes(x = r_squared)) +
  geom_density()
```

Distribution plot of $$log(\hat{\beta_0}*\hat{\beta_1}) $$

```{r}
boot_results %>% 
  ggplot(aes(x = log)) +
  geom_density()
```

95% Confidence Interval for $$\hat r^2$$ and $$log(\hat{\beta_0}*\hat{\beta_1}) $$:

```{r}
boot_results %>% 
  summarize(
    r2_ci_lower = quantile(r_squared, 0.025),
    r2_ci_upper = quantile(r_squared, 0.975),
    beta_ci_lower = quantile(log, 0.025),
    beta_ci_upper = quantile(log, 0.975)
  )
```

