---
title: "Homework 6"
author: "Yue Liu"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(modelr)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data 

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1
    )
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL")%>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```

start with one city

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")

# generalized regression model
glm(resolution ~ victim_age + victim_race + victim_sex,
    data = baltimore_df,
    family = binomial()) %>%  # need to specify distribution
  broom::tidy() %>% # estimate is reported as log odds ratio; race shows in 5 subgroups
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```

Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## Problem 2

```{r}
birthweight_df = 
  read_csv("data/birthweight.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(babysex = as.factor(case_when(babysex == 1 ~ "male", 
                                       babysex == 2 ~ "female")),
         frace = as.factor(case_when(frace == 1 ~ "White",
                                     frace == 2 ~ "Black",
                                     frace == 3 ~ "Asian",
                                     frace == 4 ~ "Puero Rican",
                                     frace == 8 ~ "Other",
                                     frace == 9 ~ "Unknown")),
         malform = as.factor(case_when(malform == 0 ~ "absent",
                                       malform == 1 ~ "present")),
         mrace = as.factor(case_when(mrace == 1 ~ "White",
                                     mrace == 2 ~ "Black",
                                     mrace == 3 ~ "Asian",
                                     mrace == 4 ~ "Puero Rican",
                                     mrace == 8 ~ "Other",
                                     mrace == 9 ~ "Unknown"))
         )
```

Import the data and convert `babysex`, `frace`(father's race), `mrace`(mother's race), and `malform`(presence of malformations) to factor. 

Since there is no further information on which predictors might be more significant, I used backward stepwise regression to select variables.

```{r}
my_model = lm(bwt ~ ., data = birthweight_df) %>% 
  step(direction = 'backward', trace = 0)

summary(my_model)

# glm(bwt ~ ., data = birthweight_df) %>% 
#   step(direction = 'both',
#        scope = list(lower = . ~ 1,
#                     uppwer = .~.^2),
#        trace = 0)
# 
# terms(my_model) %>% 
#   attr("term.labels") %>% 
#   str_c(., collapse =  "+") %>% 
#   str_c("bwt ~ ",.) %>% 
#   as.formula()
```

According to the results, my model will contain predictors `babysex`, `bhead`(baby's head circumference), `blength` (baby's length at birth), `delwt`(mother's weight), `fincome`(family monthly income), `gaweeks`(gestational age in weeks), `mheight`(mother's height), `mrace`(mother's race), `parity`(number of live births prior to this pregnancy), `ppwt` (mother's pre-preg weight), and `smoken` (average numbers of cigarettes smoked during pregnancy)


```{r}
cv_df = 
  crossv_mc(birthweight_df, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )
```

Fit the models.

```{r}
# cv_df = 
#   cv_df %>% 
#   mutate(
#     linear_mod = map(.x = train, ~lm(y ~ x, data = .x)),
#     smooth_mod = map(.x = train, ~gam(y ~ s(x), data = .x)),
#     wiggly_mod = map(.x = train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))
#   ) %>% 
#   mutate(
#     rmse_linear = map2_dbl(.x = linear_mod, .y = test, ~rmse(model = .x, data = .y)),
#     rmse_smooth = map2_dbl(.x = smooth_mod, .y = test, ~rmse(model = .x, data = .y)),
#     rmse_wiggly = map2_dbl(.x = wiggly_mod, .y = test, ~rmse(model = .x, data = .y))
#   )
```


